Hire Ed: Job Market Dynamics for Tenure-Track Faculty Positions in Archaeology

### 2024-09-17 analysis/paper/paper.qmd

# this doesn't work, need help to troubleshoot
EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE)

# here's the list of words of interest
community_word <- c("women","color","religion","race","age","veteran","disability")

@@

# detect if the words of interest is present or not.
EEO_clean_community_word <- 
  bind_cols(EEO_clean, df) %>% 
  rowwise() %>% 
  mutate(community_word_tally = sum(c_across(all_of(community_word)), 
                                    na.rm = T))

@@

EEO_word %>% 
  filter(n >= 20) %>% 
ggplot() +
  aes(x = reorder(word, n), y = n) +
  geom_col() +
  coord_flip() +  # Flips the axes for easier reading of text
  labs(x = "Words", y = "Frequency", title = "Word Frequency") 
```

>>>>

#word count for EEO statement
EEO_wordcount <- EEO %>%
  mutate(word_count = str_count(equal_employment_opportunity_statement, "\\S+")) %>%
  print()

jobdata_EEO_year_tally <-
  EEO_wordcount %>%
  group_by(year_ad_posted) %>%
  summarise(n = mean(word_count))

fig_ave_length_EEO_per_year <- 
ggplot(jobdata_EEO_year_tally) +
  aes(year_ad_posted,n) +
  geom_col() +
  ylab("Average length of EEO statement by year") +
  theme_minimal(base_size = 28) +
  guides(x = "none")

ggplot(EEO_wordcount) +
  aes(year_ad_posted, word_count) +
  geom_boxplot() +
  geom_quasirandom()

ggplot(jobdata_requirements_means %>% 
         filter(name == "diversity\nstatement") ) +
  aes(year_ad_posted, 
      mean_n) +
  geom_col()

# here's the list of words of interest
community_word <- c("women","color","religion","race","age","veteran","disability","citizenship","national origin","sex","gender","marital status","genetic information","breastfeeding","sexual orientation","transgender status","gender expression","gender identity","ancestry","income assignment for child support","arrest and court record","domestic or sexual violence victim status","national guard absence","visible minorities","aboriginal persons","indigenous","LGBTQ2S+","pregnancy","childbirth","faith","genetic or family medical history","medical condition","nationality","ethnicity","parental status","accent","ethnic","creed","political affiliation","immigration status")

EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE) %>%
  drop_na()

@@

# detect if the words of interest is present or not.
EEO_clean_community_word <- 
  bind_cols(EEO_clean, df) %>% 
  rowwise() %>% 
  mutate(community_word_tally = sum(c_across(all_of(community_word)), 
                                    na.rm = T)) %>% 
  bind_cols(EEO_wordcount) %>% 
  mutate(eeo_words_total_ratio = community_word_tally / word_count)

ggplot(EEO_clean_community_word) +
  aes(community_word_tally,
      word_count,
      size = eeo_words_total_ratio) +
  geom_point()

ggplot(EEO_clean_community_word) +
  aes(community_word_tally) +
  geom_histogram()
```

```{r}
ggplot(EEO_word %>% 
         filter(n > 20), 
       aes(x = reorder(word, n), 
           y = n)) +
  geom_col() +
  labs(x = "Words", 
       y = "Frequency", 
       title = "Word Frequency") +
  coord_flip()
```

```{r}
# explore QS rankings

qs_rankings <- 
  readxl::read_excel("analysis/data/raw_data/2024 QS WUR by Subject - Public Results (for qs.com)_48.xlsx", sheet = "Archaeology", skip = 12)

jobdata %>% 
  mutate(Institution = str_remove(name_of_hiring_university,
                                  " \\(.*\\)")) %>% 
  mutate(Institution = case_when(
    # modify the school name to match with the name in the QS list
    Institution == "Ohio State University-Main Campus" ~ "The Ohio State University",
  "Cambridge" ~ "University of Cambridge",
  "Cambridge University" ~ "University of Cambridge",
  "Keble College" ~ "University of Oxford",
  "University of California-Berkeley" ~ "University of California, Berkeley (UCB)",
"University of California-Los Angeles" ~ "University of California, Los Angeles (UCLA)",
"University of Tuebingen" ~ "Eberhard Karls Universität Tübingen",
"Universität Tübingen" ~ "Eberhard Karls Universität Tübingen",
"Arizona State University Campus Immersion" ~ "Arizona State University",
"Kiel University" ~ "Christian-Albrechts-University zu Kiel",
"University of Arizona" ~ "The University of Arizona",
"The Pennsylvania State University" ~ "Pennsylvania State University",
"University of Bologna" ~ "Alma Mater Studiorum - University of Bologna",
"University of Sydney" ~ "The University of Sydney",
"University of Copenhagen, Saxo Institute" ~ "University of Copenhagen",
"The University of Texas at Austin" ~ "University of Texas at Austin",

    .default = as.character(Institution)
  )) %>% 
  select(Institution) %>% 
  left_join(qs_rankings) %>% 
  drop_na(`2024`) %>% 
  distinct(Institution, .keep_all = TRUE) %>% 
  View()

@@
